---
title: "brand preference prediction"
author: "mohammed"
date: "2/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load library
```{r message=FALSE}
library(dplyr)
library(caret)
library(lattice)
library(ggplot2)
library(C50)
library(randomForest)
```

# Load dataset

```{r}
survey=read.csv2(file="surveyBelkinElago.csv",header = TRUE,sep = ";",na.strings =c(""," "),dec = ",")
```



# Assigning data types
```{r}
survey$salary=as.numeric(survey$salary)
survey$age=as.numeric(survey$age)
survey$elevel=as.factor(survey$elevel)
survey$car=as.factor(survey$car)
survey$zipcode=as.factor(survey$zipcode)
survey$credit=as.numeric(survey$credit)
survey$brand=as.factor(survey$brand)
```

# Creating 2 df, one with response and another with no response
```{r}

data1=survey %>% filter(!is.na(brand))
data2=survey %>% filter(is.na(brand))


```

# Partitioning training and testing data
```{r}
set.seed(100)
intraining=createDataPartition(data1$brand,p=.75,list=FALSE)
training=data1[intraining,]
testing=data1[-intraining,]

```





# Training C5.0 model

```{r}

set.seed(123)
ctrl<- trainControl(method = "repeatedcv",
                           number = 10,
                          repeats = 1, 
                          returnResamp="all",
                          classProbs=TRUE,
                          summaryFunction = twoClassSummary)


c50Fit <- train(x=training[1:6],
                y=training$brand,
                 method = "C5.0",
                preProc = c("center", "scale"),
                tuneLength = 2,
                trControl = ctrl,
                metric = "ROC")
```

# Testing C5.0 model
```{r}
C5Classes <- predict(c50Fit, newdata = testing)
confusionMatrix(C5Classes,testing$brand)
```






# Training randomforest model
```{r}
set.seed(123)
tuneGrid <- expand.grid(.mtry = c(1: 5))
randomFit <- train(x=training[1:6],
                   y=training$brand,
                   method = "rf",
                  preProc = c("center", "scale"),
                  trControl = ctrl,
                  metric = "ROC",
                  tuneGrid = tuneGrid
)
randomFit
```

# Test rf model



```{r}
plsClasses <- predict(randomFit, newdata = testing)
confusionMatrix(plsClasses,testing$brand)
```

# Training Knn model
```{r}
set.seed(123)

tuneGrid <- expand.grid(.k = c(1: 20))

knnFit <- train(x=training[1:6],y=training$brand,
                   method = "knn",
                   tuneGrid = tuneGrid,
                   preProc = c("center", "scale"),
                   trControl = ctrl,
                metric = "ROC"
              
            
      
                   
)
```


# Testing knn model
```{r}
knn <- predict(randomFit, newdata = testing)
confusionMatrix(knn,testing$brand)

```


# Important variables in C5.0 model
```{r}
ggplot(varImp(c50Fit))

```

# Important variables in random forest model
```{r}
ggplot(varImp(randomFit))
```

# Important variables in Knn model
```{r}
ggplot(varImp(knnFit))
```


# Compairing the three models
```{r warning=FALSE}
resamps=resamples(list(c5model=c50Fit,rfmodel=randomFit,knnmodel=knnFit))
summary(resamps)

```






# Diffrence of the models and selecting the best model
```{r}
diffs <- diff(resamps)
summary(diffs)
```


* **Random forest model and C5.0 model are similiar**
* **Knn model differ from other two model and have least roc**
* **C5.0 have comparitively higher ROC so we select C5.0 as the predicting model**

# Predicting customer's preferance 
```{r}

predi=predict(c50Fit,newdata=data2)
table(predi)

```
# Include the response to the data set
```{r}
data3=data2 %>% mutate(brand=predi)
```

# Join the data sets
```{r}
new_data=full_join(data1,data3)
summary(new_data)
```


# Finding the brand preference of customers
```{r}
ggplot(new_data,aes(brand,fill=brand))+geom_bar()+ theme_light() +
  scale_fill_manual(values = c("Belkin"="darkgreen","Elago"="orangered"))+
  labs(title = "Brand preference of customer",
        caption = "Belkin:7054 \nElago:7946")+theme(legend.text = element_text(colour="black",
                                   size=12, 
                                   face="bold"),
        plot.title =element_text(color="black",
                                 size=15, 
                                 face="bold.italic"),
        axis.title.x =element_text(color = "black",
                                   size = 14,
                                   face="plain") ,
        axis.title.y = element_text(color="black",
                                    size=12,
                                    face="bold"),
        legend.title =element_text(colour="black", 
                                   size=14,
                                   face="bold"),
        axis.text.x = element_text(face="bold", 
                                   color="darkgreen", 
                                    size=12),
          axis.text.y = element_text(face="bold",
                                     color="darkgreen", 
                                     size=10),
        plot.caption =element_text(color="black",
                                    size=12,
                                    face="bold.italic") )
```




* **customer prefer to buy Elago products more than Belkin**